### 2022-08-10 1638 art 1.1.tex
added 40 files to archive

\documentclass{amsart}
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\usepackage{hyperref,amscd}
\usepackage[shortlabels]{enumitem}
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\title{1638 / 1.1}
\author{Navidad}
\date{\today}
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\linespread{1.3}
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\begin{document}
\maketitle
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\section{Theses}
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\section{xxx}
%%%
%%%
%%%
%%%
We use \(i, n\) subscripts to index ie list things within countable agglomerates and \(\alpha,\beta,\gamma\) for uncountable ones which may be indexed ie listed. Use \(q,e,p\) variables for code strings ie ordered \(n\)-tuples of symbols. Let 
\begin{align*}
Q=q_0 &= \langle\mbox{How and when was Hon founded?}\rangle\\
q_1 &= \langle\mbox{How and when was Hon resorted by Eng?}\rangle\\
q_2 &= \langle\mbox{How and when was Hon settled by Eng?}\rangle\\
q_3 &= \langle\mbox{How and when was Hon logged by Eng?}\rangle \\
q_4 &= \langle\mbox{How and when was Hon voided by Sp?}\rangle\\
\end{align*}
and so on. Similarly let
\begin{align*}
e_0 &= \langle\mbox{How and when was Hon founded?}\rangle\\
e_1 &= \langle\mbox{How and when was Hon resorted by Eng?}\rangle\\
e_2 &= \langle\mbox{How and when was Hon settled by Eng?}\rangle\\
e_3 &= \langle\mbox{How and when was Hon logged by Eng?}\rangle \\
e_4 &= \langle\mbox{How and when was Hon voided by Sp?}\rangle\\
\end{align*}
%%%
%%%
%%%
%%%
%%%
\[
\begin{CD}
A @>a>> (Q,Q_a)\\
@VbVV	\\
C
\end{CD}
\]
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\section{xxx}
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\end{document}

### 2022-08-10 pre-git/archived-files/1638 art 1.0.tex
moved to pre-git/archived-files

\documentclass{amsart}
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\usepackage{hyperref,tikz-cd}
\usepackage[UKenglish]{babel}
\usepackage[shortlabels]{enumitem}
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\linespread{1.3}
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\title{1638 / 1.0}
\author{Navidad}
\date{\today}
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\begin{document}
\maketitle
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\section{Pre}
%%%
%%%
%%%
%%%
\subsection{Space}
Use the usual geometric model spacetime. Have events modeled as shapes and agents as line segments. Geographic spaces as shapes too. Divide objects of enquiry or discussion like.
	\[
 	\begin{tikzcd}[column sep=small]
				& S\ar[dl] \ar[dr]	& 	&	&\\
	P^\prime	&					& P\ar[dl]\ar[dr]&&\\
				&			A^\prime& 	&A\ar[dl]\ar[dr]&\\
				&					&T^\prime&	&T
	\end{tikzcd}
	\]
where \(S\) is all of spacetime, \(P\) is a clean cut of spacetime restricted by geographic and temporal boundaries, \(A\) is a fixed restricted list of line segments ie agents, \(T\) is a fixed class of events.
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\subsection{P limits}
%%%
%%%
For \(P\subset E\) we want to take a clean cut of \(E\). To make this, we want to know where to cut ie start and end for the temporal dimension, and \(x, y, z\) coordinates for the extended dimensions.
\subsubsection{Temporal limits} We want to start at the time when Bacalar was estblished ie March \(1543\) so say from and including \(1\) January \(1543\) Gregorian ie NS. We want to stop some short while after the Capture of Tris so say to and including \(31\) December \(1717\) Gregorian ie NS. Giving use \(175\) years.
\subsubsection{Extended limits} We want to include \(z\) ie height above and below the area to be demarcated to some small extent so say \(1\) mile of airspace above some arbitrary sealevel and \(1\) mile of subspace below the same arbitrary sealevel eg as measured form Earth's centre core assuming prefectly spherical globe. Now we give vertices of an \(n\)-gon on said sphere by giving breadth and width points ie \(x,y\) coordinates in the form of GPS coordinates. Eg going clockwise -
	\begin{enumerate}
	\item Start at some point currently in Nicaragua ie the southernmost point of the greatest extent the Mosquito Shore ever had eg mouth of Rio San Juan,
	\item Run along the midpoint of the Caribbean and Pacific coasts of the Central American landmass or isthmus until first reaching or hitting a point in Peten, Guatemala,
	\item Take a beeline to the first or southermost point on Rio Chixoy which forms part of the Mexico-Guatemala border,
	\item Follow this border until reaching the Tabasco-Chiapas border,
	\item Follow that border until reaching the coast,
	\item From this point make a northern beeline some good number of nautical miles into the Gulf of Mexico,
	\item Trace the coast from this point, around the Yucatan peninsula, all the way to Cape Camaron Light in present-day Honduras, being sure to include offshore cayes etc,
	\item From this point of Camaron make a beeline to some point a good number of natical miles north of the Cayman Islands,
	\item And make another beeline to the easternmost point north a good number of nautical miles north of the easternmost point of Jamaica, and trade that coast to its westernmost point,
	\item See map for more as got tired.
	\end{enumerate}
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\subsection{A limits}
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\subsection{T limits}
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\subsection{T contents}
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
%%%
\end{document}

### 2023-10-01 work/oct-23/draft-tab.tex
add to work/oct-23
add draft0 content, with vars revisions, and some supplementary section contant, to draft tex file

\begin{table}[h]% \centering not needed for amsart documentclass
\caption{Series which would prove useful in version 1.0.0 or a later version.}% must top table for amsart
\label{t:series}% should follow caption for amsart
\begin{tabularx}{\textwidth}{lScL}
\toprule
series & of & 1.0.0 & note\\
\midrule
calendar & records in significant or major collections & yes & Known major records collections include some in the AGI, ARS, TNA. Noted calendars include Burdon's \titleit{Archives}, the \titleit{CSP}, the \titleit{CDI}.\\
calendar & records in minor collections & no & Various identified in historical literature and version 0.n.0. Some catalogued. Noted calendars include \emph{some} of the Camden Series.\\
calendar & rare literature & no & Rare literature includes rare books, scarce periodicals. Noted calendars include \emph{some} of the Camden Series.\\
catalogue & historical literature & yes & Noted catalogues include xx.\\
catalogue & non-historical literature & no & Non-historical literature includes eg archaeological, geographical literature. Noted catalogues include xx.\\
catalogue & official literature & no & Official literature includes eg Crown reports, parliamentary papers. Noted catalogues include xx.\\
catalogue & non-official literature & no & Non-official literature includes eg press. Noted catalogues include xx.\\
catalogue & manuscripts & yes & Noted catalogues include xx.\\
chronicle & pre-Columbian events & may & Noted chronicles include xx.\\
chronicle & Columbian events & yes & Noted chronicles include xx.\\
compendium & pre-statistical or historical statistics & yes & Noted compendia include the \titleit{BHS}, the \titleit{HSUS}.\\
compendium & statistical or modern statistics & yes & Noted compendia include xx.%for modern as in 19th to 20th cent
\\
dictionary & identities of natural persons & may & Noted dictionaries include Oxford's \titleit{DNB}, the RAH's \titleit{DBE}.\\
dictionary & identities of non-natural persons & no & Noted dictionaries include xx.\\
gazetteer & identities of natural points or shapes & no & Noted gazetteers include Enciso's \titleit{Suma de Geographia}.\\
gazetteer & identities of non-natural points or shapes & may & Noted gazetteers include xx.\\
\bottomrule
\addlinespace[\belowrulesep]% suggested by booktabs package
\multicolumn{4}{p{\textwidth}}{\tabnote{Header row---\mention{1.0.0} is version 1.0.0. First column---\mention{calendar} includes \emph{both} those which describe or summarise items or their contents \emph{and} those which further transcribe or translate their contents; \mention{catalogue} includes bibliographies and the like; \mention{compendium} includes statistical series, digests, and the like; \mention{dictionary} includes directories and the like; \mention{gazetteer} includes geographical dictionaries, pilots, maps, atlases, and the like. Second column---append `of use to historical reasoning' to all entries, and read \mention{literature} as publications. Third column---\mention{may} is maybe or perhaps. Fourth column---\mention{notable} as in relatively salient to the author during the building of version 0.n.0.}}
\end{tabularx}
\end{table}

### 2023-10-02 work/oct-23/draft-tab.tex
add to work/oct-23
draft and draft-tab tex files had additions and possible subtractions during copy editing

@@
 calendar & rare literature & no & Rare literature includes rare books, scarce periodicals. Noted calendars include \emph{some} of the Camden Series.\\
+calendar & oral history & no & Noted calendars include xx.\\
 catalogue & historical literature & yes & Noted catalogues include xx.\\
